Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-11 analysis/paper/paper.Rmd
Clean up table formatting, digits, caps, etc.

```{r data_available, tab.id="da", tab.cap="Article ratings for data availability where '0', not specified or mentioned in publication to '3', Freely available online to anonymous users for foreseeable future (_e.g._, archived using Zenodo, dataverse or university library or some other proper archiving system).", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(data_avail) %>%
  adorn_pct_formatting() %>% 
  select(-percent) %>% 
  rename(`Data availability` = data_avail,
         Percent = valid_percent) %>% 
  flextable() %>%
  colformat_num(na_str = "NA") %>% 
  autofit()
```

@@

rrpp_software %>% 
  tabyl(software_used) %>%
  adorn_pct_formatting() %>% 
  select(c(-percent, -valid_percent)) %>% 
  rename(`software used` = software_used) %>% 
  arrange(-n) %>% 
  slice(seq_len(14)) %>% 
  drop_na() %>% 
  flextable() %>%
  autofit()
```

@@

```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(reproducibility_score) %>%
  adorn_pct_formatting() %>%
  rename(score = reproducibility_score) %>%
  flextable() %>%
  autofit()
```

>>>>

```{r data_available, tab.id="da", tab.cap="Article ratings for data availability where '0', not specified or mentioned in publication to '3', Freely available online to anonymous users for foreseeable future (_e.g._, archived using Zenodo, dataverse or university library or some other proper archiving system).", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(data_avail) %>%
  adorn_pct_formatting() %>% 
  select(-valid_percent) %>% 
  rename(`Data availability` = data_avail,
         Percent = percent) %>% 
  flextable() %>%
  colformat_num(na_str = "NA") %>% 
  autofit()
```

@@

rrpp_software %>% 
  tabyl(software_used) %>%
  adorn_pct_formatting() %>% 
  select(c(-percent, -valid_percent)) %>% 
  rename(`Software Used` = software_used) %>% 
  arrange(-n) %>% 
  slice(seq_len(14)) %>% 
  drop_na() %>% 
  flextable() %>%
  autofit()
```

@@

```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(reproducibility_score) %>%
  adorn_pct_formatting(digits = 1) %>%
  rename(Score = reproducibility_score, Percent = percent) %>%
  flextable() %>%
  autofit()
```
